\documentclass[ipfjes-centre,letterpaper,pagesize,UScommercial9]{scrlttr2}

\renewcommand{\normalsize}{\fontsize{10}{12}\selectfont} 

\begin{document}

\begin{letter}{Title Name \\ Address1 \\ Address2 \\ Address3 \\ Postcode}

    \setkomavar{subject}{RE: Idiopathic Pulmonary Fibrosis Job Exposures Study (IPF JES)}

\opening{Dear Title Name,}

     I am writing to invite you to participate in a study of job exposures in Idiopathic pulmonary fibrosis (IPF) we are running at our hospital. You are being invited because you recently attended our respiratory clinic and were diagnosed with IPF. 
     
     The study involves an interview to measure historic job exposures and a blood test to investigate susceptibility genetics. 
     
    I enclose the participant information sheet. Participation is entirely voluntary and whether or not you decide to participate will not change your clinical care. 
    
    You do not need to take any action now. If you are interested in the study then the research team will discuss it with you at your next outpatient appointment.

    If you wanted to ask the research team anything they are happy for you to contact them (details below).

    \vspace{1cm}
    \begin{centering}
    \textbf{
    IPF JES Research Team \\  
    National Heart and Lung Institute, \\
    Room G39 Emmanual Kaye Building, \\
    1b Manresa Road, London, SW3 6LR\\
    carl.reynolds@imperial.ac.uk \\
    07737 904 807 \\
    }
    \end{centering}
    \vspace{1cm}

\closing{Yours sincerely}

     \vfill \hfill [IPF JES Participant Case Letter Version 0.4]


\end{letter}
\end{document}

